---
title: "Effects of Health Indicators on Economic Output"
author: "TheStatian"
date: "12/3/2015"
output: ioslides_presentation
---

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(dplyr)
library(ggplot2)
library(stringr)
library(GGally)
```

```{r, message=FALSE, echo=FALSE, warning=FALSE}
dataset <- read.csv("WHO.csv", stringsAsFactors = FALSE, na.strings = c(NA, NULL))
```

#Research Question
##Research Question

What are the correlations between economic status of countries and the health indicators of countries? And how are they correlated?

# Our Dataset
## Our Dataset

- Took data from the World Health Organization (WHO)
- Includes social, economic, health, and political variables
- Used GNI (Gross National Income) per capita
    - GNI = GDP + income earned by citizens in foreign economy - income earned by foreigners in domestic economy
    - GNI more applicable because it focuses on solely domestic factors
    - per capita takes population into account
    
# World Differences in Economic Growth
## GNI Classifications

- Low income: $1,035 or less
- Lower middle income: $1,036 to $4,085
- Upper middle income: $4,086 to $12,615
- High income: $12,616 or more

```{r echo=FALSE}
dataset$income_group <- cut(dataset$GNI_per_capita, 
                       breaks = c(-Inf, 1035, 4085, 12615, Inf), 
                       labels = c("LOW INCOME", "LOWER MIDDLE INCOME", "UPPER MIDDLE INCOME", "HIGH INCOME"), 
                       right = FALSE)

```

```{r echo=FALSE}
dataset %>%
  group_by(income_group) %>%
  summarise(count = n())
```

## GNI Classifications

```{r echo=FALSE}
incomeplot <- ggplot(dataset, aes(x = income_group)) + 
  geom_histogram()
incomeplot + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

# Graphing the Impacts on Economic Status
## Avoiding Colinearity

- split variables into five sections
    - Government Expenditure on Health
    - Preventative Treatment
    - Quality of Child Health Treatment
    - Disease and Disease Mortality Rates
    - Density of Health Workers
- Variables likely to be colinear within each group, but less so between each one
- Used the variable with the highest $R^2$ value to construct full model

## Government Expenditure on Health

```{r echo=FALSE, warning=FALSE}
ggplot(data = dataset, aes(x = GNI_per_capita, y = Per_capita_government_expenditure_on_health)) +
  geom_point(position = "jitter") +
  stat_smooth(method = "lm")
```

## Government Expenditure on Health

$\widehat{GNIpercapita} = 4224.34 + 12.60\widehat{PerCapitaGovernmentExpenditureOnHealth}$

- A nation whose government spends nothing on health would be expected to have a GNI of 4224.34 (Upper Middle Income).
- Each increase in 1 of per-capita government health expenditure would increease GNI by 12.60
    - GNI includes overall government expenditure, so this makes sense with the definition of the variable

## Preventative Treatment

```{r echo=FALSE, warning=FALSE}
ggplot(data = dataset, aes(x = GNI_per_capita, y = Women_who_have_had_mammography)) +
  geom_point(position = "jitter") +
  stat_smooth(method = "lm")
```

## Preventative Treatment

$\widehat{GNIpercapita} = 3386.05 + 407.86\widehat{WomenWhoHaveHadMammography}$

- A country where no women have had mammographies would be expected to have a GNI of 3386.05 (Lower Middle Income)
- An increase of 1 in the percentage of women who have had mammographies would increase the GNI by 407.86
    - increased health expenditure due to treatment costs

## Quality of Child Health Treatment

```{r echo=FALSE, warning=FALSE}
ggplot(data = dataset, aes(x = GNI_per_capita, y = Infant_mortality_rate_per_1000_live_births_both_sexes)) +
  geom_point(position = "jitter") +
  stat_smooth(method = "lm")
```

## Quality of Child Health Treatment

$\widehat{GNIpercapita} = -41501.61 +$ $783.99\widehat{InfantMortalityRatePer1000LiveBirthsBothSexes}$

- Infant mortality is positively correlated with GNI
- A country with a 0 infant mortality rate would have a GNI of -41501.61
    - unrealistic, but this would classify the country as Low Income
- Countries with higher infant mortality rates likely spend more on healthcare to mitigate the effects
    - would raise GNI due to increased government expenditure
- Infant deaths may be linked towards the poorer areas in countries with high GNI and high income inequality

## Disease and Disease Mortality Rates

```{r echo=FALSE, warning=FALSE}
ggplot(data = dataset, aes(x = GNI_per_capita, y = Colon_and_Rectum_cancer_new_cases_per_100_000_women)) +
  geom_point(position = "jitter")+
  stat_smooth(method = "lm")
```

## Disease and Mortality Rates

$\widehat{GNIpercapita} = -467.96 +$ $1005.17\widehat{ColonAndRectumCancerNewCasesPer100000Women}$

- With 0 Colon and Rectal Cancer Cases, we would expect GNI to be -467.96. However, a country would not realistically have a negative GNI.
- Increased Colon and Rectal Cancer Case rates likely increase the amount of both expenditure to cure the disease and aleviate present symptoms
    - A larger rate would increase GNI by increasing the amount of money used to combat the disease (positive correlation) 

## Density of Health Workers

```{r echo=FALSE, warning=FALSE}
ggplot(data = dataset, aes(x = GNI_per_capita, y = Nursing_and_midwifery_personnel_density_per_10000_population)) +
  geom_point(position = "jitter") +
  stat_smooth(method = "lm")
```

## Density of Health Workers

$\widehat{GNIpercapita} = 1837.37 +$ $251.19\widehat{NursingAndMidwiferyPersonnelDensityPer10000Population}$

- A country with 0 nurses or midwives would be expected to have a GNI of 1837.37 (Low Income)
- Each increase in 1 unit of density would increase the GNI by 251.19
    - would increase the flow of money due to the increased workforce, adding to the consumption and overall income
    

# Constructing a Full Model
## Constructing a Full Model

- Each variable explains the variance best within each cohort, but not necessarily overall
```{r echo=FALSE, message=FALSE}
full_model_gni_health <- lm(GNI_per_capita ~ Per_capita_government_expenditure_on_health + Women_who_have_had_mammography + Infant_mortality_rate_per_1000_live_births_both_sexes + Colon_and_Rectum_cancer_new_cases_per_100_000_women + Nursing_and_midwifery_personnel_density_per_10000_population, data = dataset)
```

```{r}
full_model_gni_health$call
AIC(full_model_gni_health)
```

## Constructing a Full Model
```{r echo=FALSE, message=FALSE, error=FALSE}
final_model_gni_health <- step(full_model_gni_health, direction = "forward")
```

```{r}
AIC(final_model_gni_health)
```

## Constructing a Full Model

- Since the AIC did not change as a result of forward selection, the full model with all 5 variables explains the variance best

$\widehat{GNIpercapita} = -11444.022 +$ $10.017\widehat{PerCapitaGovernmentExpenditureOnHealth} -$ $3.457\widehat{WomenWhoHaveHadMammography} +$ $230.872\widehat{InfantMortalityRatePer1000LiveBirthsBothSexes} -$ $23.755\widehat{ColonAndRectumCancerNewCasesPer100000Women} +$ $35.033\widehat{NursingAndMidwiferyPersonnelDensityPer10000Population}$

- a country essentially must have some expenditure on overall health, or else its GNI per capita would likely be -11444.022

# Implications
## Implications

- Government should increase expenditure on health due to the positive correlation between government healthe expenditure and GNI
    - expenditure should be equitable to overall population
- Variables considered only affect economic growth, yet their implications are more complex
    - social factors like HIV prevalence, infant mortality, and other cancer rates would have effects on policy making
    - governments may not have the available capital or ability to borrow to increase spending on health


# Limitations and further explorations
## Limitations and further explorations

- Further studies could explore the percentage of the population below poverty line and household income

- Some variables may be more available from countries with the resources to collect
    - Cancer rates, nursing and midwife densities, and mammography rates may be collected in more developed nations
    - Political climate in some regions may reduce the amount of data reported to the WHO

- different measurement/data collection method    

